Survival Probability Difference M-F

### 2025-01-31 code/R/Survival_Probability_Difference_MF.Rmd
formatting update

# Plot the difference with credible intervals
ggplot(time_summaries_df, aes(x = time_period, y = mean)) +
  geom_point(color = "blue") +
  geom_errorbar(aes(ymin = lower95, ymax = upper95), width = 0.2, color = "blue") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  labs(
    title = "Difference in Survival Probabilities (Male - Female) Over Time",
    x = "Time Period",
    y = "Difference in Survival Probability"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

###############################################################################
# 5. Plot the Differences with Correct Time Order
###############################################################################

@@

# Create the plot
difference_plot <- ggplot(time_summaries_df, aes(x = time_period, y = mean)) +
  geom_point(color = "blue", size = 2) +  # Increased point size for better visibility
  geom_errorbar(aes(ymin = lower95, ymax = upper95), width = 0.2, color = "blue") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  labs(
    title = "Difference in Survival Probabilities (Male - Female) Over Time",
    x = "Time Period",
    y = "Difference in Survival Probability"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for readability
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold")  # Center and style the title
  ) +
  scale_x_discrete(limits = paste0("time_", 1:T))  # Ensure correct order on x-axis

@@

# Save the plot to a file
ggsave("difference_in_survival_probabilities.png", plot = difference_plot, width = 10, height = 6, dpi = 300)

>>>>

# plot

@@

# Create the plot
difference_plot <- ggplot(time_summaries_df, aes(x = time_period, y = mean)) +
  geom_point(color = "blue", size = 2) +  # Increased point size for better visibility
  geom_errorbar(aes(ymin = lower95, ymax = upper95), width = 0.2, color = "blue") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  labs(
    title = "Difference in Survival Probabilities (Male - Female) Over Time",
    x = "Time Period",
    y = "Difference in Survival Probability"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for readability
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold")  # Center and style the title
  ) +
  scale_x_discrete(limits = paste0("time_", 1:T))  # Ensure correct order on x-axis

@@

# Save the plot to a file
ggsave("/Users/johnimperato/Desktop/Mossy-Pond_companion/difference_in_survival_probabilities.png", plot = difference_plot, width = 10, height = 6, dpi = 300)
